\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-07-30 docs/parco13/paper.tex

>>>>

\begin{figure}
  \begin{center}
  \begin{minipage}{.4\columnwidth}
    \begin{tabular}{cc}
      timing table for sphere & 123, \\
    \end{tabular}
  \end{minipage}
  \hspace{.05\columnwidth}
  \includegraphics[width=.4\columnwidth]{../figs_misc/sphere_partition5}
\end{center}
\caption{Partition of the spherical Example 2 between five MPI processors, indicated
  by the color scale, at simulated time $T = 1$.  The partition shows the mesh equator,
  while the refinement is invariant under the number of processors and the partition
and follows the front, which is not aligned with the equator.}
\label{fig:spherical}
\end{figure}
To demonstrate a multiblock connectivity, we include results for Example 2 in
\Fig{spherical}.
